### 2024-09-06 skripsi/bab1.tex
research design and computational model, fix root file latex

\chapter{INTRODUCTION}
\section{Background}\label{sec:background} %pelabelan ini opsional, biar bisa di klik kalo mengarahkan ke section tertentu.
\noindent Partial differential equations (PDE) are a common tool widely used in the modern scientific understanding and many engineering processes. This is because many systems can be described by the way they change and often this can be more intuitive. As an example, think of someone heating up a large frying pan on a gas stove. To describe how the pan heats up when the center is right above the burner, one can say that the center would heat up first followed by its surroundings. Eventually the pan would not heat up any further. Also notice that the edges of the pan would always be cooler than the center. However, once a more complex setup is introduced such as an uneven heat source or more complex materials with different heat rates of transferring heat it becomes much harder to describe how the pan heats up. A more useful way to describe the system is using the heat equation. For a temperature function \(u\left(\vb{x},t\right)\) of spatial coordinates vector \(\vb{x}\) and time \(t\), the generalized heat equation is defined in \lccref{eq:heat_equation}.
\begin{equation} \label{eq:heat_equation}
    \pdv{u}{t}=\divergence{\left(\alpha \gradient u\right)}
\end{equation}
The divergence operator \(\divergence \) denotes sum of all first spatial derivatives. In three dimensions this is \(\divergence=\pdv{\cdot}{x_1}+\pdv{\cdot}{x_2}+\pdv{\cdot}{x_3}\). And the gradient operator \(\gradient \) is the vector of all first spatial derivatives which in three dimensions is \(\gradient{f} = {\begin{bmatrix}\pdv{f}{x_1} & \pdv{f}{x_2} & \pdv{f}{x_3}\end{bmatrix}}^{\intercal}\). This equation says that the rate at which the temperature changes in time \(\pdv{u}{t}\) is proportional to how different the differences in temperature of a spot in the pan with its surroundings \(\laplacian{u}\) multiplied with thermal diffusivity parameter \(\alpha \). One example of an insight this gives is that given a homogeneous material (\(\alpha \) is constant) and the stove outputs heat at a constant rate the temperature will no longer change for a particular point once the temperature difference is constant. In other words once the function \(u\left(\vb{x},t\right)\) at some time \(t > 0 \) approaches a linear function in space, the temperature at all spots will no longer change in time. Mathematically this is because the time derivative is zero if the second spatial derivatives are also zero. Intuitively this is because once the temperature distribution approaches linear, the current spot on the pan is outputting as much heat it is getting. This insight is an example of why PDEs are useful.

@@

\section{Limitations}
\noindent This work is limited to the following:
\begin{enumerate}
    \item Functions the model works with are only continuous functions.
    \item Hardware used in this project is limited to the standard offering on \url{kaggle.com} as of \today.
    \item The basis functions are limited to Fourier basis.
\end{enumerate}

>>>>

% !TEX root = ./skripsi.tex
\chapter{INTRODUCTION}
\section{Background}\label{sec:background} %pelabelan ini opsional, biar bisa di klik kalo mengarahkan ke section tertentu.
\noindent Partial differential equations (PDE) are a common tool widely used in the modern scientific understanding and many engineering processes. This is because many systems can be described by the way they change and often this can be more intuitive. As an example, think of someone heating up a large frying pan on a gas stove. To describe how the pan heats up when the center is right above the burner, one can say that the center would heat up first followed by its surroundings. Eventually the pan would not heat up any further. Also notice that the edges of the pan would always be cooler than the center. However, once a more complex setup is introduced such as an uneven heat source or more complex materials with different heat rates of transferring heat it becomes much harder to describe how the pan heats up. A more useful way to describe the system is using the heat equation. For a temperature function \(u\left(\vb{x},t\right)\) of spatial coordinates vector \(\vb{x}\) and time \(t\), the generalized heat equation is defined in \lccref{eq:heat_equation}.
\begin{equation} \label{eq:heat_equation}
    \pdv{u}{t}=\divergence{\left(\alpha \gradient u\right)}
\end{equation}
The divergence operator \(\divergence \) denotes sum of all first spatial derivatives. In three dimensions this is \(\divergence=\pdv{\cdot}{x_1}+\pdv{\cdot}{x_2}+\pdv{\cdot}{x_3}\). And the gradient operator \(\gradient \) is the vector of all first spatial derivatives which in three dimensions is \(\gradient{f} = {\begin{bmatrix}\pdv{f}{x_1} & \pdv{f}{x_2} & \pdv{f}{x_3}\end{bmatrix}}^{\intercal}\). This equation says that the rate at which the temperature changes in time \(\pdv{u}{t}\) is proportional to how different the differences in temperature of a spot in the pan with its surroundings \(\laplacian{u}\) multiplied with thermal diffusivity parameter \(\alpha \). One example of an insight this gives is that given a homogeneous material (\(\alpha \) is constant) and the stove outputs heat at a constant rate the temperature will no longer change for a particular point once the temperature difference is constant. In other words once the function \(u\left(\vb{x},t\right)\) at some time \(t > 0 \) approaches a linear function in space, the temperature at all spots will no longer change in time. Mathematically this is because the time derivative is zero if the second spatial derivatives are also zero. Intuitively this is because once the temperature distribution approaches linear, the current spot on the pan is outputting as much heat it is getting. This insight is an example of why PDEs are useful.

@@

\section{Limitations}
\noindent This work is limited to the following:
\begin{enumerate}
    \item Functions the model works with are only continuous functions.
    \item Hardware used in this project is limited to the standard offering on \url{kaggle.com} as of \today{}.
    \item The basis functions are limited to Fourier basis. % TODO: change this if more basis functions are added
    \item Modeled fields are compact or dense meaning not sparse. Sparse observations or other data are assimilated using other methods.
\end{enumerate}

### 2024-09-06 skripsi/bab3.tex
research design and computational model, fix root file latex

\chapter{METODOLOGI PENELITIAN}
\label{sec:metodologi_penelitian}

Secara umum, metode penelitian yang digunakan pada pekerjaan penelitian disampaikan pada bab ini. Judul bab tidak harus seperti yang dituliskan. Dalam kata lain bisa diubah sesuai kebutuhan.

\section{Model Komputasi}
\noindent The DeepONet architecture contains an element that is difficult to optimize.
% \begin{mini}
%   {W_b}{y=(W_b\cdot f+b_b)^\top\cdot(W_t\cdot v+b_t)+\xi
% \end{mini}

\begin{mini!}|s|
{\substack{W_b,b_b,W_t,b_t,\xi}}{\frac{1}{2}\Vert W_b\Vert_F^2 + \frac{1}{2}\Vert W_t\Vert_F^2 + \frac{c}{2}\sum_{i=1}^{l}\xi_i^2} {}{}
\addConstraint{y_i}{=(W_b f_i+b_b)^\top(W_t v_i+b_t)+\xi_i,\quad}{i=1,\ldots,l}
\end{mini!}

\begin{equation}
  \begin{aligned}
    L(W_b,b_b,W_t,b_t,\xi;\alpha)= {} & \frac{1}{2}\Vert W_b\Vert_F^2 + \frac{1}{2}\Vert W_t\Vert_F^2 +\frac{c}{2}\sum_{i=1}^{l}\xi_i^2 \\ &+ \sum_{i=1}^{l}\alpha_i(y_i-\xi_i-(W_b f_i+b_b)^\top(W_t v_i+b_t))
  \end{aligned}
\end{equation}
\begin{equation}
  \begin{aligned}
    \pdv{L(W_b,b_b,W_t,b_t,\xi;\alpha)}{W_b}                               & = 0                                                                                \\
    \frac{2}{2}W_b + 0 + 0 - \sum_{i=1}^{l}\alpha_i((W_t v_i+b_t)f_i^\top) & = 0                                                                                \\
    W_b - \sum_{i=1}^{l}\alpha_i((W_t v_i+b_t)f_i^\top)                    & = 0                                                                                \\
    W_b                                                                    & = \sum_{i=1}^{l}\alpha_i(W_t v_i f_i^\top+b_t f_i^\top)                            \\
    W_b                                                                    & = \sum_{i=1}^{l}(\alpha_i W_t v_i f_i^\top)+ \sum_{i=1}^{l}(\alpha_i b_t f_i^\top) \\
    W_b                                                                    & = W_t \sum_{i=1}^{l}(\alpha_i v_i f_i^\top)+ b_t \sum_{i=1}^{l}(\alpha_i f_i^\top) \\
    W_b                                                                    & = W_t \sum_{i=1}^{l}(\alpha_i v_i f_i^\top)+ b_t \sum_{i=1}^{l}(\alpha_i f_i^\top) \\
  \end{aligned}
\end{equation}
\begin{equation}
  \begin{aligned}
    \pdv{L(W_b,b_b,W_t,b_t,\xi;\alpha)}{W_t}                                        & = 0                                                                                                                                                                                    \\
    0 + \frac{2}{2}W_t + 0 - \sum_{i=1}^{l}\alpha_i((W_b f_i + b_b)v_i^\top)        & = 0                                                                                                                                                                                    \\
    W_t - \sum_{i=1}^{l}\alpha_i((W_b f_i + b_b)v_i^\top)                           & = 0                                                                                                                                                                                    \\
    W_t                                                                             & = \sum_{i=1}^{l}\alpha_i(W_b f_i v_i^\top + b_b v_i^\top)                                                                                                                              \\
    W_t                                                                             & = \sum_{i=1}^{l}\alpha_i((\sum_{j=1}^{l}\alpha_j(W_t v_j f_j^\top + b_t f_j^\top)) f_i v_i^\top+b_b v_i^\top)                                                                          \\
    W_t                                                                             & = \sum_{i=1}^{l}(\sum_{j=1}^{l}(\alpha_i\alpha_jW_t v_j f_j^\top f_i v_i^\top + \alpha_i\alpha_j b_t f_j^\top f_i v_i^\top) + \alpha_i b_b v_i^\top)                                   \\
    W_t                                                                             & = \sum_{i=1}^{l}(\sum_{j=1}^{l}(\alpha_i\alpha_jW_t v_j f_j^\top f_i v_i^\top) + \sum_{j=1}^{l}(\alpha_i\alpha_j b_t f_j^\top f_i v_i^\top) + \alpha_i b_b v_i^\top)                   \\
    W_t - \sum_{i=1}^{l}\sum_{j=1}^{l}\alpha_i\alpha_jW_t v_j f_j^\top f_i v_i^\top & = \sum_{i=1}^{l}(\sum_{j=1}^{l}(\alpha_i\alpha_j b_t f_j^\top f_i v_i^\top) + \alpha_i b_b v_i^\top)                                                                                   \\
    W_t(I - \sum_{i=1}^{l}\sum_{j=1}^{l}\alpha_i\alpha_j v_j f_j^\top f_i v_i^\top) & = \sum_{i=1}^{l}(\sum_{j=1}^{l}(\alpha_i\alpha_j b_t f_j^\top f_i v_i^\top) + \alpha_i b_b v_i^\top)                                                                                   \\
    W_t                                                                             & = \sum_{i=1}^{l}(\sum_{j=1}^{l}(\alpha_i\alpha_j b_t f_j^\top f_i v_i^\top) + \alpha_i b_b v_i^\top) (I - \sum_{i=1}^{l}\sum_{j=1}^{l}\alpha_i\alpha_j v_j f_j^\top f_i v_i^\top)^{-1} \\
    W_t                                                                             & = \sum_{i=1}^{l}(\alpha_i(\sum_{j=1}^{l}(\alpha_j b_t f_j^\top f_i) + b_b)v_i^\top ) (I - \sum_{i=1}^{l}\sum_{j=1}^{l}\alpha_i\alpha_j v_j f_j^\top f_i v_i^\top)^{-1}                 \\
  \end{aligned}
\end{equation}
\begin{equation}
  \begin{aligned}
    \pdv{L(W_b,b_b,W_t,b_t,\xi;\alpha)}{b_b}        & = 0 \\
    0 + 0 + 0 - \sum_{i=1}^{l}\alpha_i(W_t v_i+b_t) & = 0 \\
    \sum_{i=1}^{l}\alpha_i(W_t v_i+b_t)             & = 0
  \end{aligned}
\end{equation}
\begin{equation}
  \begin{aligned}
    \pdv{L(W_b,b_b,W_t,b_t,\xi;\alpha)}{b_t}        & = 0 \\
    0 + 0 + 0 - \sum_{i=1}^{l}\alpha_i(W_b f_i+b_b) & = 0 \\
    \sum_{i=1}^{l}\alpha_i(W_b f_i+b_b)             & = 0
  \end{aligned}
\end{equation}
\begin{equation}
  \begin{aligned}
    \pdv{L(W_b,b_b,W_t,b_t,\xi;\alpha)}{\xi}                         & = 0        \\
    0 + 0 + \frac{2c}{2}\sum_{i=1}^{l}\xi_i - \sum_{i=1}^{l}\alpha_i & = 0        \\
    \sum_{i=1}^{l}c\xi_i - \alpha_i                                  & = 0        \\
    c\xi_i                                                           & = \alpha_i \\
  \end{aligned}
\end{equation}
\begin{equation}
  \begin{aligned}
    \pdv{L(W_b,b_b,W_t,b_t,\xi;\alpha)}{\alpha}                         & = 0 \\
    0 + 0 + 0 + \sum_{i=1}^{l}y_i-\xi_i-(W_b f_i+b_b)^\top(W_t v_i+b_t) & = 0 \\
    \sum_{i=1}^{l}y_i-\xi_i-(W_b f_i+b_b)^\top(W_t v_i+b_t)             & = 0
  \end{aligned}
\end{equation}

>>>>

% !TEX root = ./skripsi.tex
\chapter{Research Methodology}\label{sec:research_methodology}

% Secara umum, metode penelitian yang digunakan pada pekerjaan penelitian disampaikan pada bab ini. Judul bab tidak harus seperti yang dituliskan. Dalam kata lain bisa diubah sesuai kebutuhan.

\section{Research Design}
\noindent This study is carried out under the framework of a research design. In this section, this design will be laid out and explained. The design includes the process from the beginning to the end of the overall study. The research design is visually depicted in \lccref{fig:research_design_diagram}.

\begin{figure}[h]
  \centering
  \tikzfig{figures/research_design_diagram}
  \caption{Research design diagram}\label{fig:research_design_diagram}
\end{figure}

The study is carried out in 9 main phases. Each phase has a specific aim to accomplish such that the subsequent phases are able to proceed. Each phase is explained as follows:

\begin{enumerate}
  \item Problem Specification

        The first phase of the study is dedicated to specifying and identifying the problem to be studied and will define the solution this study sets out to discover.

  \item Literature Review

  \item Design of Computational Model

  \item Implementation of Computational Model

  \item Planning of Experimental Scenarios

  \item Data Generation and Retrieval

  \item Data Preprocessing

  \item Experiments

  \item Analysis and Discussion

\end{enumerate}
